### 2016-09-07 rebuttal.txt

We try to provide a complete description of the method, but since we
are also distributing our implementation, this makes sense.  Therefore
we have added installation/configuration instructions in Appendix A.

> 2. The discussion of latency/timing is somewhat confusing, and I
> believe it omits what I (and other investigators) consider to be the
> most crucial metric of detection performance – the variation in
> latency from the onset of the targeted syllable to the firing of the
> TTL pulse.

We had already characterised the timing from the completion of the
target recognition region to the firing of the TTL pulse--this is what
we define as "Jitter" (line 27, Section Quantification.Timing
(beginning around line 342), and also extensively throughout the
document).  We have tried to clean up those references and clarify
our description.

> Charlesworth et al. (“Learning the microstructure of successful
> behavior”) showed that learning after white noise targeting is
> temporally localized at less than 10 msec timescale. Furthermore, in
> my own and other labs, the key predictor of whether online targeting
> will successfully drive learning is the standard deviation of
> detections/triggers relative to syllable onset, with syllable onset
> defined by some measure of sound amplitude for each individual
> iteration of the syllable. I believe (and please correct me if I’m
> wrong) that the song alignment technique used here does not provide
> this statistic on a syllable-by-syllable basis.

@@

> Most
> importantly, they do not do a life bird test.

I'm not sure what this means.  The fibre photometry test is a live
bird test (and ongoing research in our lab uses the detector with
great success), but of course all quantitative tests must be done on
recordings in order to systematically analyse accuracies of various
detectors.

> In fact, they haven't included calls, wing flaps, and other noises
> in their training or testing sets.  Thus, it seems there is no
> realistic evaluation of their system.

That is an excellent point!  We have remedied this.  See the paragraph
around line 160.  Also, the new Results/Accuracy graph (Fig. 3) shows
accuracy figures including lots of cage noise samples (about half an
hour's worth).  Correct detections and incorrect detections have both
somewhat decreased from our earlier results.

@@

> e.g. fig 1 increase font size of labels

Thanks.  Done.

> Line 189: It takes so long to train a network with just 2 to 4 hidden
> neurons?

Big data sets, and we made little effort to optimise offline
(training) speed!  But we changed the training algorithm and now
things are about 10 times faster.

### 2016-09-07 main.tex
Take out last (?) reference to Fibre Photometry experiment.

% Insert additional author notes using the symbols described below. Insert symbol callouts after author names as necessary.
% 
% Remove or comment out the author notes below if they aren't used.
%
% Primary Equal Contribution Note
%\Yinyang These authors contributed equally to this work.
Author \textsuperscript{a}~contributed the original MATLAB and LabVIEW implementations and most of the manuscript.
\textsuperscript{b}~contributed the Swift implementation and its description herein, helped debug the training code, and measured the timing for most of the detectors.
\textsuperscript{c}~performed the fibre photometry experiment, wrote several types of filter-bank software against which we compared, made suggestions for the neural network detector, and reformatted the MATLAB code for distribution.
\textsuperscript{d}~provided a stream of suggested techniques, metrics, and goals.

@@

We evaluate the time taken from the complete presentation of each
instance of the target syllable to the firing of the detector's TTL
pulse.  For example, if the recognition region is 30 ms long and the
target trigger point is at 200 ms with respect to the corpus of
aligned songs, then when the detector has seen the region from
170--200 ms, it should recognise the syllable.  If for a given
presentation of the song the detector fires at 203 ms, we take the
latency on that trial to be 3 ms.

@@

We allowed our training software to allocate our default of 4 hidden
units per syllable, and computed a new FFT every 1.5 ms.  Because our
timing test files are designed for our stereo playback software,
allowing only one channel for the ground-truth pulse, we trained one
detector for each syllable for the following results.  In order to
eliminate the large number of variables involved in microphone, cage,
playback and re-digitising, we evaluated the neural network's accuracy
directly on the digitised recording.  When training and runtime data
are gathered on the same hardware setup, this is the digital signal
that the detector will see---only the non-song data may be different.

>>>>

% Insert additional author notes using the symbols described below. Insert symbol callouts after author names as necessary.
% 
% Remove or comment out the author notes below if they aren't used.
%
% Primary Equal Contribution Note
%\Yinyang These authors contributed equally to this work.
Author \textsuperscript{a}~contributed the original MATLAB and LabVIEW implementations and most of the manuscript.
\textsuperscript{b}~contributed the Swift implementation and its description herein, helped debug the training code, and measured the timing for most of the detectors.
\textsuperscript{c}~wrote several types of filter-bank software against which we compared, made suggestions for the neural network detector, and reformatted the MATLAB code for distribution.
\textsuperscript{d}~provided a stream of suggested techniques, metrics, and goals.

@@

We evaluate the time taken from the complete presentation of each
instance of the target syllable to the firing of the detector's TTL
pulse.  For example, if the target trigger point is at 200 ms with
respect to the corpus of aligned songs, and if the detection region is
30 ms long, then when the detector has seen the region from 170--200
ms, it should recognise the syllable.  If for a given presentation of
the song the detector fires at 203 ms, we take the latency on that
trial to be 3 ms.

@@

We allowed our training software to allocate our default of 4 hidden
units per syllable, and computed a new FFT every 1.5 ms.  Because our
timing test files are designed for our stereo playback software,
allowing only one channel for the ground-truth pulse, we trained one
detector for each syllable for the following results.  In order to
eliminate the large number of variables involved in microphone, cage,
playback and re-digitising, we evaluated the neural network's accuracy
directly on the digitised recording.  When training and runtime data
are gathered on the same hardware setup, this is the digital signal
that the detector will see---only the non-song data may be different.
%Accuracy \marginpar{Should be! Verify! And/or explain that there is a bug in the LabVIEW implementation, if there in fact is. ALSO need to present a picture of the test syllable or etc \dots} is identical across the three detectors.
\noprint{
  Typical confusion matrices for these syllables are:

  \vspace{8pt}\par\noindent
  \begin{tabular}{r|cc}
    $t^*_1$
    & \multicolumn{2}{c}{True} \\ 
    & pos & neg \\ 
    \hline  Detected pos & 99.96451\% & 0.000298\%\\ 
    neg & 0.0355\% & 99.99970\%\\ 
  \end{tabular}
  \vspace{8pt}\par\noindent
  \begin{tabular}{r|cc}
    $t^*_2$ & \multicolumn{2}{c}{True} \\ 
    & pos & neg \\ 
    \hline  Detected pos & 99.92903\% & 0.000596\%\\ 
    neg & 0.0710\% & 99.99940\%\\ 
  \end{tabular}
  \vspace{8pt}\par\noindent
  \begin{tabular}{r|cc}
    $t^*_3$ & \multicolumn{2}{c}{True} \\ 
    & pos & neg \\ 
    \hline  Detected pos & 99.68062\% & 0.00194\%\\ 
    neg & 0.319\% & 99.99806\%\\ 
  \end{tabular}
  \vspace{8pt}\par\noindent
  \begin{tabular}{r|cc}
    $t^*_4$ & \multicolumn{2}{c}{True} \\ 
    & pos & neg \\ 
    \hline  Detected pos & 99.82257\% & 0.00239\%\\ 
    neg & 0.177\% & 99.99761\%\\ 
  \end{tabular}
  \vspace{8pt}\par\noindent
  \begin{tabular}{r|cc}
    $t^*_5$ & \multicolumn{2}{c}{True} \\ 
    & pos & neg \\ 
    \hline  Detected pos & 99.78708\% & 0\\ 
    neg & 0.213\% & 100\%\\ 
  \end{tabular}
  \vspace{8pt}\par\noindent
  \begin{tabular}{r|cc}
    $t^*_6$ & \multicolumn{2}{c}{True} \\ 
    & pos & neg \\ 
    \hline  Detected pos & 99.71611\% & 0.00552\%\\ 
    neg & 0.284\% & 99.99448\%\\ 
  \end{tabular}
  \vspace{8pt}\par\noindent
}
